Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-10-30 paper.tex
update

 \item To propose a PSO-based service composition model that utilise the proposed quality model. In PSO, each particle represent a weighted graph sorts out an optimised service queue as an indirect representation of web service composition with the consideration of comprehensive quality, and this service queue is further decoded using a graph building algorithm to generate a final solution.

@@

The remains of this paper are organized as the following: Sect. \ref{background} provides the background on the semantic web service composition, and related works; Sect. \ref{qswsc_approach} presents an overview of comprehensive quality awareness semantic automated web service composition consisting of comprehensive quality evaluation model and PSO-based service composition algorithm; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents the results and analysis of the experiment; Sect. \ref{conclusion} is the paper conclusion.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is a given task input or input set to get the desired Task output or output set, it typically refers to users' functional requirement; another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. Meanwhile, a output set is initialised and updated with found services output, which could be denoted as  $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$. The Output Set is used to discovery all related services until the desired $T_{Output}$ found in the updated Output Set. The discovery process normally results in more than one solutions. Service selection is to select one of those composite solution considering the closest QoS to $T_{QoS}$. To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional requests. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$. The web service matching process is to pair the output and input concepts of two services according to the Taxonomy(Tax) within an ontology (O). To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}: We defined two web services associated with parameters in a particular domain. $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ are defined in.

\begin{itemize}
\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ S_{output} \in S_{1} \equiv S_{input}S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
\item \textit{Plugin} ($\sqsubseteq$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($S_{output} \in S_{1} \sqsubseteq S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$.
\item \textit{Subsume} ($\sqsupseteq$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($S_{output} \in S_{1} \sqsupseteq S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$.
\item \textit{Fail} ($\perp$). Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($S_{output} \in S_{1} \perp S_{input} \in S_{2}$), if none of the previous matches discovered.
\end{itemize}

Note that, to find relevant services to automatically form suitable and applicable service compositions for a given goal, we consider Exact, Plugin and Fail match types in our paper. Therefore, these three robust matches will be used to discover web service candidates for service composition.

\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS, which covers aspects in non-functional requirements. This problem have been explored in both single objective and multi-objectives optimisation. Ideally, customers prefer lowest execution cost with highest response time and reliability. According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other \cite{zeng2003quality}. Here we consider two composite constructs: both sequence and parallel construts are used in building the composite flow, which are described as follows:

@@

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Figure \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed in the meantime. The QoS aggregation value in total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution. This construct is presented in Figure \ref{parallel}.

@@

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model comprehensive quality awareness automated semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the five steps included. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts. The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: a graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected while calculating matchmaking quality that will be explained in Subsect. \ref{qualityModel}. Step 4,5: The selection of web services is performed over the PSO algorithm in subSect. \ref{pso_algorithm}, which is used to find best particle location mapped back to a service queue for building graph solutions considering comprehensive quality. This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
\subsection{Semantic matchmaking}

>>>>

 \item To propose a PSO-based service composition model that utilise the proposed quality model. In PSO, weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively represent the solutions of semantic web service composition as particles, which are decoded from an optimised service queue with the consideration of comprehensive quality.

@@

The remains of this paper are organised as the following: Sect. \ref{background} provides the background on the semantic web service composition, and related works; Sect. \ref{qswsc_approach} presents an overview of comprehensive quality-aware semantic automated web service composition consisting of comprehensive quality evaluation model and PSO-based service composition algorithm; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents and analyses the experiment; Sect. \ref{conclusion} concludes our work.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is a given task input or input set to get the desired Task output or output set. It typically refers to users' functional requirement. Another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. If no atomic web service could satisfy the composite goal, a combination of web services will be found concretely to meet $Comp.G$. Firstly, a output set is initialised and updated with found services output, which could be denoted as $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$. The Output set is used to discover all related services until the desired $T_{Output}$ found in the updated Output Set. The discovery process normally results in more than one service compositions. Therefore, Service selection is to select one of those composite solutions considering the best QoS according to $T_{QoS}$. To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model defined in \ref{qualityModel} for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional requests. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Taxonomy\}$. A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an Ontology (O). To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}. To understand these levels, let us define two web services associated with parameters in a particular domain. $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S_{2}$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$. The matching levels to be considered are:

\begin{itemize}
\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ S_{output} \in S_{1} \equiv S_{input}S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($S_{output} \in S_{1} \sqsubseteq_{n} S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($S_{output} \in S_{1} \sqsupseteq_{n} S_{input} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
\item \textit{Fail} ($\perp$). Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($S_{output} \in S_{1} \perp S_{input} \in S_{2}$), if none of the previous matches discovered.
\end{itemize}

Note that, to find relevant services for service compositions according to a given goal, we consider Exact, Plugin, Subsume and Fail match types in our paper. Therefore, these matches will be used to discover web service candidates for service composition with consideration of the threshold $\alpha$ to enhance the accuracy and efficiency in our proposed the comprehensive quality-aware model in Sect.\ref{semantic_matchmaking}

\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS, which covers aspects in non-functional requirements. This problem has been explored in both single objective and multi-objectives optimisation problems. Customers prefer lowest execution cost with highest response time and reliability so that it could be involved as a single objective optimisation problem while cost and reliability of web service are two conflicting objectives that could be optimised simultaneously in multi-objective problem. According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other in a service composition \cite{zeng2003quality}. Here we consider two composite constructs: sequence and parallel constructs, in building the composite flow. The QoS calculation models are described as follows:

@@

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Figure \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed in the meantime. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution. This construct is presented in Figure \ref{parallel}.

@@

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model comprehensive quality awareness automated semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the five steps included. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts. The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: a graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected while calculating matchmaking quality that will be explained in Subsect. \ref{qualityModel}. Step 4,5: The selection of web services is performed over the PSO algorithm in subSect. \ref{pso_algorithm}, which is used to find best particle location mapped back to a service queue for building graph solutions considering comprehensive quality. This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
\subsection{Semantic matchmaking} \label{semantic_matchmaking}
